%---------------------------------------------------------
\cventry
{Lead AI Engineer}
{Plutto (YC S22)}
{Santiago, Chile}
{May 2025 - Aug 2025}
{
\begin{cvitems}
    \item Led development of an AI agent to extract insights from company data, supporting new product features and improved decision-making capabilities.
    \item Spearheaded MLOps practices to improve two production models: enhanced a user-facing classification model and optimized a back-office model to reduce overfitting and improve performance.
    \item Designed and implemented an LLM cost tracking system and led cloud infrastructure development on GCP.
    \item Drove data-driven practices across teams through documentation and tools, including leading initial work on a data catalog for better metric visibility.
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Staff Machine Learning Engineer (MLE - Generative AI Platform)}
{NeuralWorks (LATAM Airlines)}
{Santiago, Chile}
{Nov 2023 - Feb 2025}
{
\begin{cvitems}
    \item Developed and deployed a scalable Dataform wrapper, replacing a complex legacy Python/Kubernetes pipeline system. This streamlined data workflow creation, reducing errors and accelerating iteration.
    \item Implemented a RAG system using Apache Beam/GCP Dataflow to efficiently process large document sets for summarization and question answering, providing a flexible workflow.
    \item Built a GenAI Ops framework to automate packaging and deployment of tested inference modules (pkl), fully compatible with existing MLOps to support both classic ML and GenAI.
    \item Enabled Gemini fine-tuning within the existing MLOps framework, letting teams train custom GenAI models using familiar workflows and go live fast without retraining across GCP environments.
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Machine Learning Engineer (MLE - Business Booster)}
{NeuralWorks (LATAM Airlines)}
{Santiago, Chile}
{Jan 2023 - Oct 2023}   
{
\begin{cvitems}
    \item Built and deployed a vector similarity-based recommendation system to personalize the home page for new users during cold starts, recommending trending content based on user interactions and content popularity.
    \item Drove development initiatives for audience expansion, fraud prevention, and destination recommendation by building and maintaining key ML infrastructure and providing expert support.
    \item Developed and maintained the MLOps framework, creating reusable libraries for model training/deployment, resolving CI/CD issues, and implementing features to streamline ML product development.
    \item Developed low-latency APIs using optimized data retrieval to provide real-time model predictions, working around the absence of a feature store.
    \item Mentored Data Scientists on agile workflows and best practices to accelerate model iteration.
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Developer Engineer (SDE - Backend)}
{Grupo Central}
{Santiago, Chile}
{Oct 2022 - Nov 2022}
{}

%---------------------------------------------------------
\cventry
{Software Engineer (SDE - Full Stack)}
{Betterfly}
{Santiago, Chile}
{Jul 2022 - Sep 2022}
{
\begin{cvitems}
    \item Designed and implemented a single-table DynamoDB data model, optimizing it for future data team ingestion via composite keys and strategic indexing.
    \item Implemented Clean Architecture in a serverless microservices framework (NestJS/TypeScript) for a B2B flex benefits application, improving code maintainability, testability, and developer context switching.
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Data Engineer (DE)}
{Betterfly}
{Santiago, Chile}
{Jan 2022 - Jun 2022}
{
\begin{cvitems}
    \item Developed and deployed data products (dashboards, pipelines) and cloud infrastructure, ensuring data availability and reliability.
    \item Designed, implemented, and maintained Python ETL pipelines for efficient large-scale data processing.
    \item Orchestrated DevOps workflows for critical production data products, ensuring CI/CD using tools like bitbucket pipelines.
    \item Developed an MLOps template to streamline/automate custom model deployment to the cloud.
    \item Migrated Staging Data VPC to Production Data AWS Environment, enhancing data security/access control via IAM roles and security groups.
\end{cvitems}
}
%---------------------------------------------------------
